---
title: "psychedelic text color in Rmarkdown"
description: |
  Using CSS and Rmarkdown to create psychedelic colors.
author:
  - name: Daniel Jachetta
    url: {}
date: 06-28-2020
css: styles.css
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = FALSE)
```



```{r}
library(ggplot2)
library(cowplot)
library(magick)
ggdraw() +
  draw_image("lego.png") 
```



In order to get this specific distill article blog to point to the CSS file, It first needs to be assigned in the YAML header. A simplified YAML header is below. 

````markdown
---
output: 
  html_document:
    css: style.css
---
````

The .CSS file has to reside within the same directory as the .Rmd file, or atleast have a relative file path if it were to reside in a child directory.

Below is the contents of the **`style.css`**. The *"d-article"* attribute was found by using the inspect element tool in Firefox, with a few trials and errors. Other Rmarkdown formats will require the appropriate attribute to be used in place of the *"d-article"* attribute.

````css
   d-article{
   width:100%;
   color:#313131;
   font-size:18px;
   position: absolute;
   -webkit-animation:colorchange 20s infinite alternate;}
   
   @-webkit-keyframes colorchange {
   0% {color: blue;}
   10% {color: #8e44ad;}
   20% {color: #1abc9c;}
   30% {color: #d35400;}
   40% {color: blue;}
   50% {color: #34495e;}
   60% {color: blue;}
   70% {color: #2980b9;}
   80% {color: #f1c40f;}
   90% {color: #2980b9;}
   100% {color: pink;}}
````

And that is it! This gives the webpage a dynamic feel, even though the changing text color isn't necessary, it was fun to learn how to create this type of effects.