---
title: "Effective Interactive Data Visualization with R"
description: |
  With Rmarkdown, R, DataTables, and plotly
author:
  - name: Daniel Jachetta
    url: {}
date: 06-15-2020
css: styles.css
categories:
  - plotly
  - ggplot2
  - Datatables
output:
  distill::distill_article:
    self_contained: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```




This is the official first blog post of this blog! We will start out with a simple tutorial inspired from [Interactive web-based data visualization with R, plotly, and shiny by Carson Sievert Published by CRC press](https://plotly-r.com/).

In this tutorial, we will use 3 packages:

1. ggplot2
2. plotly
3. DT

let's load them into R.

```{r echo = TRUE}
library(ggplot2)
library(plotly)
library(DT)
```

Below is the data visualization we will create with interactive capabilities, accompanied by a dynamic Datatable.

```{r}
ggplot(mpg,aes(displ,hwy))+geom_point(aes(color = cyl)) + geom_smooth(se = TRUE)
```
We will be using the `mpg` dataset for this example, which comes inside ggplot2. The first function we use is the `highlight_key()` function from plotly, which was written by the book author Carso Sievert. This function creates an object based on a primary key. In this example, we use the entire data frame.

```{r echo=TRUE}
m<-highlight_key(mpg)
```

Next we create a ggplot2 plot with `geom_point()`, where we map the cylinder of each car to the `color` arguement, and `geom_smooth` for the standard error line.

```{r echo=TRUE}
p<-ggplot(m,aes(displ,hwy))+geom_point(aes(color = cyl)) + geom_smooth(se = TRUE)
```

Next, `highlight()` is the function used for the brushing/highlighting multiple plots or points. we used the argument "plotly_selected".

```{r echo=TRUE}
gg<-highlight(ggplotly(p),"plotly_selected")
```


Finally we pass the previous 3 lines of code to `crosstalk::bscols()`, which is using Bootstrap and HTML to align our Datatable. The code below is all we have to write, 4 lines of code give us an interactive plot with brushing, and a dynamic table with sorting and searching.


```{r echo=TRUE}
m<-highlight_key(mpg)
p<-ggplot(m,aes(displ,hwy))+geom_point(aes(color = cyl)) + geom_smooth(se = TRUE)
gg<-highlight(ggplotly(p),"plotly_selected")
crosstalk::bscols(gg,DT::datatable(m))
```

