---
title: "Creating gauge charts with googleviz"
description: |
  Using googleViz package to create gauge charts.
author:
  - name: Daniel Jachetta
    url: {}
date: 08-01-2020
css: styles.css
categories:
  - GoogleViz
output:
  distill::distill_article:
    self_contained: false
---


```{r}
library(ggplot2)
library(cowplot)
library(magick)
ggdraw() +
  draw_image("gauge.png") 
```

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = FALSE)
```

This article is a short demo how to create gauge charts utilizing the *Googleviz* package.

First lets load our libaries we will need for this tutorial

> library(googleVis) <br> library(reshape2)

*Note the capitalization of the `GoogleVis` package.*

Now we need some data to visualize. Let's pretend we are a manager for a small team, and get weekly reports. 
This gauge chart will tell us our employee attendance every day for the previous week.

We created a small set of data with Day of the week and attendance count. We had to do a little bit of data manipulation to get the data in the 
right format for visualizing. The documentation for the package can be [found here.](https://www.rdocumentation.org/packages/googleVis/versions/0.6.0/topics/gvisGauge) These charts are best viewed in a web browser, and sometimes I have had issues when trying to generate these charts without internet connection, so keep that in mind. Each gauge displays its respective value in the bottom of the gauge. I think gauge charts are great KPI(Key performance indicators) visualize tools.


````R
library(googleVis)
library(reshape2)

#creating data
staff_count <- c(12, 13, 15, 16, 14)
the_day <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

#manipulating data
the_day <- as.factor(the_day)
staff <- melt(data.frame(the_day,staff_count))
staff <- as.data.frame(staff)
staff <- staff[,c(1,3)]

#creating visualization
Gauge <-  gvisGauge(staff,chartid='September_23_to_27_2019',
                    options=list(min=0, max=16, greenFrom=13,
                                 greenTo=16, yellowFrom=7, yellowTo=13,
                                 redFrom=0, redTo=7, width=750, height=200))
#plotting visualization
plot(Gauge)
````

```{r}
library(ggplot2)
library(cowplot)
library(magick)
ggdraw() +
  draw_image("gauge.png") 
```

And that's it! Only about 15 lines of code to create awesome Google gauge charts in R!

